AI-Based Detection of Jamming Attacks In 6G Drone Networks

### 2024-09-13 article.tex
Updated citation

This would prove useful in a variety of fields: from autonomous soil and crop health assessment as well as irrigation in agriculture, 
delivery of life saving supplies and locating of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation.

@@

>>>>

This would prove useful in a variety of fields: from autonomous soil and crop health assessment as well as irrigation in agriculture, 
delivery of life saving supplies and locating of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation \cite{DroneCommHassija}.

@@

\bibitem[Hassija et al.(2021)]{DroneCommHassija}
Hassija, V.; Kumar, R.; Gupta, H.; Singh, S.; Sharma, P. Fast, Reliable, and Secure Drone Communication: A Comprehensive Survey. {\em IEEE Communications Surveys and Tutorials} {\bf 2021}, {\em 23}, 2802--2832. https://doi.org/10.1109/COMST.2021.3097916.
